A Comparison of Graph Processing Systems

### 2020-09-21 documentation/paper/sections/results/results.tex
most introductions done
galois time comparison init
todos in results und discussion

\subsection{Results}
\todo{Einleitung}

@@

On a plus side, setup of the frameworks Polymer and Ligra was straight forward and did not require any special treatment.

@@

\subsubsection{Comparison of a Single-Node to the Distributed Cluster}
\begin{table}
	\caption{Execution Times on a SingleNode vs. 5-Node Distributed Cluster}
	\label{tbl:execTimeComparison}
	\renewcommand{\arraystretch}{1.2}
	\centering
	\begin{tabular}{ccr@{\tabskip 1 \tabcolsep}r
	r@{\tabskip 1 \tabcolsep}r
	r@{\tabskip 1 \tabcolsep}r}
		\toprule
		&&\multicolumn{2}{c}{\bf Galois}&\multicolumn{2}{c}{\bf Gemini}&\multicolumn{2}{c}{\bf Giraph}\\
		\cmidrule{3-4}\cmidrule{5-6}\cmidrule{7-8}
		&\bf Graph&1N&5N&1N&5N&1N&5N\\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf SSSP}}&flickr & 0.3 & 2.4 & 0.6 & 2.5 & 38.8 & 42.6 \\
		& orkut & 0.8 & 4.2 & 13.9 & 17.3 & 135.9 & 60.4 \\
		& wikipedia & 1.8 & 14.2 & 48.5 & 74.5 & 377.2 & 100.8 \\
		& twitter & 10.8 & 40.0 & 383.0 & 391.1 & - & 349.9 \\
		& rMat27 & 16.0 & 39.0 & 563.5 & 386.0 & - & 565.8 \\
		& friendster & 14.4 & 58.5 & 742.6 & 568.9 & - & 444.0 \\
		& rMat28 & 27.8 & 71.5 & 1236.7 & 792.0 & - & 1180.2 \\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf BFS}}& flickr & 0.6 & 2.3 & 0.7 & 2.4 & 38.9 & 41.9 \\
		& orkut & 0.9 & 4.0 & 12.5 & 13.8 & 128.2 & 58.1 \\
		& wikipedia & 2.4 & 13.2 & 44.9 & 60.9 & 360.7 & 95.1 \\
		& twitter & 14.2 & 37.9 & 355.0 & 293.2 & - & 322.3 \\
		& rMat27 & 14.6 & 34.4 & 540.8 & 305.3 & - & 539.2 \\
		& friendster & 12.8 & 47.6 & 708.4 & 450.2 & - & 412.3 \\
		& rMat28 & 33.1 & 67.1 & 1178.7 & 634.3 & - & 1135.6 \\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf PR}}& flickr & 0.3\txtdagger & 2.6 & 0.7 & 2.2 & 45.6 & 44.1 \\
		& orkut & 0.7\txtdagger & 8.0 & 13.1 & 19.4 & 561.3 & 106.2 \\
		& wikipedia & 1.7\txtdagger & 206.5 & 44.4 & 54.4 & 1501.3 & 252.6 \\
		& twitter & 8.7\txtdagger & 910.9 & 359.9 & 363.5 & - & 1200.2 \\
		& rMat27 & 19.2\txtdagger & 1287.4 & 536.3 & 376.3 & - & 1369.5 \\
		& friendster & 20.4\txtdagger & 593.3 & 716.5 & 591.1 & - & 1655.0 \\
		& rMat28 & 46.0\txtdagger & 2540.2 & 1188.5 & 774.2 & - & - \\
		\bottomrule
		\multicolumn{8}{l}{(\txtdagger) Results of Galois Pull shown.}
	\end{tabular}
\end{table}
Until now, we have only compared the frameworks with each other, under the same setup circumstances. Hence, a comparison of the same framework, in single-node versus distributed setup is the content of this section.
Of course only frameworks that were tested in both setups are shown.
We focus primarily on the results of the execution times, the data can be seen in \autoref{tbl:execTimeComparison}. We show the results of Galois Push for the 5-node cluster in the table, since it is faster than Pull.

>>>>

\subsection{Results}
Ahead of the discussion of the results a few of the issues we encountered while testing are mentioned. Afterwards the benchmark results for SSSP, BFS, PR and the speedup of Galois given a varying number of threads are discussed in that order.

@@

On a plus side, setup of the frameworks Polymer and Ligra was straight forward and did not require any special treatment.
\todo{Gemini? Außerdem sollte hier noch ein bisschen was hin, die beiden Zeilen sehen ja nur traurig aus.}

@@

\subsubsection{Comparison of a Single-Node to the Distributed Cluster}
\begin{table}
	\caption{Execution Times in Seconds on a SingleNode vs. 5-Node Distributed Cluster}
	\label{tbl:execTimeComparison}
	\renewcommand{\arraystretch}{1.2}
	\centering
	\begin{tabular}{ccr@{\tabskip 1 \tabcolsep}r
	r@{\tabskip 1 \tabcolsep}r
	r@{\tabskip 1 \tabcolsep}r}
		\toprule
		&&\multicolumn{2}{c}{\bf Galois}&\multicolumn{2}{c}{\bf Gemini}&\multicolumn{2}{c}{\bf Giraph}\\
		\cmidrule{3-4}\cmidrule{5-6}\cmidrule{7-8}
		&\bf Graph&1N&5N&1N&5N&1N&5N\\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf SSSP}}&flickr & 0.3 & 2.4 & 0.6 & 2.5 & 38.8 & 42.6 \\
		& orkut & 0.8 & 4.2 & 13.9 & 17.3 & 135.9 & 60.4 \\
		& wikipedia & 1.8 & 14.2 & 48.5 & 74.5 & 377.2 & 100.8 \\
		& twitter & 10.8 & 40.0 & 383.0 & 391.1 & - & 349.9 \\
		& rMat27 & 16.0 & 39.0 & 563.5 & 386.0 & - & 565.8 \\
		& friendster & 14.4 & 58.5 & 742.6 & 568.9 & - & 444.0 \\
		& rMat28 & 27.8 & 71.5 & 1236.7 & 792.0 & - & 1180.2 \\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf BFS}}& flickr & 0.6 & 2.3 & 0.7 & 2.4 & 38.9 & 41.9 \\
		& orkut & 0.9 & 4.0 & 12.5 & 13.8 & 128.2 & 58.1 \\
		& wikipedia & 2.4 & 13.2 & 44.9 & 60.9 & 360.7 & 95.1 \\
		& twitter & 14.2 & 37.9 & 355.0 & 293.2 & - & 322.3 \\
		& rMat27 & 14.6 & 34.4 & 540.8 & 305.3 & - & 539.2 \\
		& friendster & 12.8 & 47.6 & 708.4 & 450.2 & - & 412.3 \\
		& rMat28 & 33.1 & 67.1 & 1178.7 & 634.3 & - & 1135.6 \\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf PR}}& flickr & 0.3\txtdagger & 2.6 & 0.7 & 2.2 & 45.6 & 44.1 \\
		& orkut & 0.7\txtdagger & 8.0 & 13.1 & 19.4 & 561.3 & 106.2 \\
		& wikipedia & 1.7\txtdagger & 206.5 & 44.4 & 54.4 & 1501.3 & 252.6 \\
		& twitter & 8.7\txtdagger & 910.9 & 359.9 & 363.5 & - & 1200.2 \\
		& rMat27 & 19.2\txtdagger & 1287.4 & 536.3 & 376.3 & - & 1369.5 \\
		& friendster & 20.4\txtdagger & 593.3 & 716.5 & 591.1 & - & 1655.0 \\
		& rMat28 & 46.0\txtdagger & 2540.2 & 1188.5 & 774.2 & - & - \\
		\bottomrule
		\multicolumn{8}{l}{(\txtdagger) Results of Galois Pull shown.}
	\end{tabular}
\end{table}
Until now, we have only compared the frameworks with each other, under the same setup circumstances. Hence, a comparison of the same framework, in single-node versus distributed setup is the content of this section.
Of course only frameworks that were tested in both setups are shown.
We focus primarily on the results of the execution times, the data can be seen in \autoref{tbl:execTimeComparison}. We show the results of Galois Push for the 5-node cluster in the table, since it is faster than Pull.
